Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-03-25 Journal1/_-4ex/Response.tex

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. By utilizing the comments, we enhanced our paper and eliminated problems.

%\begin{longtable}{|p{0.975\textwidth}|}
%\hline \hline
%\RaggedRight
%\cellcolor{green!10}
%[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.
%\\
%\hline
%\end{longtable}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The paper proposes resolving the problem of resource allocation to network slices by using a new algorithm applied to the reformulation of the problem. The results seem promising but the paper has some issues. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for this manuscript's careful and thorough reading. We hope that the responses provided will ease the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``First, the structure of the paper makes it somewhat hard to follow and there are some mistakes in the text. A proofread is required before it can be accepted for publication.   ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
According to this comment, we have modified the introduction and checked the entire text and correct mistakes. We have shortened the state of the arts and introduced our goal briefly before the main contribution section. We removed additional information and talked more about our work. Also, we added some figures to describe incomprehensible parts. In addition, we provide further explanations.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``Although the paper demonstrates its claims, the relaxation of conditions from the original problem formulation is not well justified. It is not clear why the initial formulation of the problem is not feasible and the reformulated makes it feasible while retaining some level of quality of the solutions given. A deeper analysis of both formulations must be presented. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would appreciate your comments to enhance and clarify this section of the paper.

The problem in (13) is feasible and has feasibility points discussed in Subsection IV-B, and we introduce a fast algorithm (i.e., Algorithm 3 in Subsection IV-B) for feasibility points. Although the problem is feasible, it is not convex and challenging to solve. Problem in (13) is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$. By relaxing the variables, the problem is still non-convex and non-trivial to solve. Inspiring by Stackelberg fomrulation, we reformulate the equation in (13g) to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs. We formulatre $M_s$ as the followers in Stackelberg Competition, and power and PRB assignment as the the leaders. So, the new problem has two variables: power and PRB assignment. This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds in (15). The objective function and constraints of the problem are convex and can be solved by the Lagrangian function. After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs in each slice ($M_s$). We made changes in Subsection III-A, accordingly.

### 2022-03-25 Journal1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (3)/pr.tex
add paper 2

Taking advantage of virtual radio access networks (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. Due to O-RAN, flexibility, openness, and lower operational costs will be possible. O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).

@@

Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Depending on QoS, each service requires its slice of the network.
The eMBB service fulfills the demand for high capacity and throughput. The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency. mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads 

@@

\textcolor{MidnightBlue}{This paper considers a number of user equipments (UEs) requesting one of these types of services with different QoS. We would like to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}

\textcolor{MidnightBlue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks. O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (CRAN). With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly. The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts. Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}

\textcolor{MidnightBlue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.}

\textcolor{MidnightBlue}{This paper aims to design a RAN slicing technology for the O-RAN architecture. }
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

@@

\textcolor{MidnightBlue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC. As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.}
\subsection{Related Literature}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
\textcolor{MidnightBlue}{The purpose of this paper is twofold. First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
In this paper, we would like to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing. We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}

In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:

@@

\item \textcolor{MidnightBlue}{We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers. Therefore, we focus on obtaining the optimal number of VNFs in each layer of the O-RAN architecture. }
\item \textcolor{MidnightBlue}{Different services need to consider varying QoS conditions, including delay, power, and throughput. According to the number of activated VNFs and the throughput of the users, we calculate the end-to-end processing delay of the system.

@@

\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.

@@

\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.

>>>>

Taking advantage of virtual radio access networks (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. Using O-RAN architecture, flexibility, openness, and lower operational costs would be achievable in the network. O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).

@@

5G wireless systems are designed to provide three possible type of services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). To achieve the QoS, each service requires its slice from the network.
The eMBB service fulfills the demand for high capacity and throughput. The URLLC services include  autonomous vehicles, tactile internet, remote surgery services, and other services of high reliability and low latency. mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads 

@@

\textcolor{MidnightBlue}{This paper considers a number of user equipments (UEs) requesting one of these types of services with specific QoS requirment. We would like to study the RAN slicing problem where service isolation is taken into account.}

\textcolor{MidnightBlue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of RAN. O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (CRAN). With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly. CRAN divides the RAN into two major parts, the radio remote head (RRH) and baseband unit (BBU). Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}

\textcolor{MidnightBlue}{O-RU is a logical node that contains RF and lower PHY. Moreover, O-DU expresses a logical node with higher PHY, MAC, and RLC. In addition, O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.}

%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

@@

\textcolor{MidnightBlue}{This paper aims to formulate RAN slicing for O-RAN architecture. This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC. As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.}
\subsection{Related Literature}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) are performed in the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
\textcolor{MidnightBlue}{The purpose of this paper is twofold. First and foremost, our goal is to design a system in the O-RAN architecture with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
In this paper, we would like to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the open and flexible O-RAN architecture.
The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing. We also convexify and solve complex problems to obtain optimal resources.}

In this paper, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:

@@

\item \textcolor{MidnightBlue}{We have consider the processing delay and the VNF resources needed for the slice compared to other papers. Therefore, we focus on obtaining the optimal number of VNFs in each layer of the O-RAN architecture. }
\item \textcolor{MidnightBlue}{Different services require different QoS levels, including delay, power, and throughput. According to the number of activated VNFs and the throughput of the users, we calculate the end-to-end processing delay of the system.

@@

\item The main problem is mixed-integer non-linear programming that is non-trivial to solve.
We deploy a two-step iterative algorithm to solve it.

@@

\item We reformulate and simplify the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use Lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple Knapsack problem and solved by the Greedy algorithm.
\item A discussion on the selection of the initial point and the feasible region for the numerical results are provided. We introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
